Formalization, Mechanization and Automation of \\ G\"{o}del's Proof of God's Existence\thanks{This work has been supported by the German Research Foundation under grant BE2501/9-1.}

### 2017-09-03 Papers/2013/ArXiv/GodProof-Abstract.tex
bibtex instead of biber

\usepackage[
    firstinits=true,
     backend=biber, 
     natbib=true,
     isbn=false,
     doi=true,
     url=false,
    style=numeric
]{biblatex}
\addbibresource[label=bibs]{Bibliography.bib}
\addbibresource[label=bibs]{chris.bib}

@@

\small

\printbibliography

>>>>

% \usepackage[
%     firstinits=true,
%      backend=bibtex, 
%      natbib=true,
%      isbn=false,
%      doi=true,
%      url=false,
%     style=numeric
% ]{biblatex}
% \addbibresource[label=bibs]{Bibliography.bib}
% \addbibresource[label=bibs]{chris.bib}

@@

\footnotesize

\begin{thebibliography}{10}

\bibitem{Adams}
R.M. Adams.
\newblock Introductory note to *1970.
\newblock In {\em {Kurt G\"odel: Collected Works Vol. 3: Unpublished Essays and
  Letters}}. Oxford University Press, 1995.

\bibitem{AndersonGettings}
A.C. Anderson and M.~Gettings.
\newblock G\"odel ontological proof revisited.
\newblock In {\em {G\"odel'96: Logical Foundations of Mathematics, Computer
  Science, and Physics: Lecture Notes in Logic 6}}, pages 167--172. {Springer},
  1996.

\bibitem{B16}
Matthias Bentert, Christoph Benzm{\"u}ller, David Streit, and Bruno
  Woltzenlogel~Paleo.
\newblock Analysis of an ontological proof proposed by {Leibniz}.
\newblock In Charles Tandy, editor, {\em Death and Anti-Death, Volume 14: Four
  Decades after Michael Polanyi, Three Centuries after G.W. Leibniz}. Ria
  University Press, 2016.

\bibitem{B9}
C.~Benzm{\"u}ller and L.C. Paulson.
\newblock Exploring properties of normal multimodal logics in simple type
  theory with {LEO-II}.
\newblock In {\em {Festschrift in Honor of {Peter B. Andrews} on His 70th
  Birthday}}, pages 386--406. College Publications, 2008.

\bibitem{J23}
C.~Benzm{\"u}ller and L.C. Paulson.
\newblock Quantified multimodal logics in simple type theory.
\newblock {\em Logica Universalis (Special Issue on Multimodal Logics)},
  7(1):7--20, 2013.

\bibitem{LEO-II}
C.~Benzm{\"u}ller, F.~Theiss, L.~Paulson, and A.~Fietzke.
\newblock {LEO-II} - a cooperative automatic theorem prover for higher-order
  logic.
\newblock In {\em Proc. of IJCAR 2008}, volume 5195 of {\em LNAI}, pages
  162--170. Springer, 2008.

\bibitem{C42}
Christoph Benzm{\"u}ller.
\newblock {G\"{o}del's} ontological argument revisited -- findings from a
  computer-supported analysis (invited).
\newblock In Ricardo~Souza Silvestre and Jean-Yves B\'eziau, editors, {\em
  Handbook of the 1st World Congress on Logic and Religion, Jo\~ao Pessoa,
  Brazil}, page~13, 2015.
\newblock (Invited abstract).

\bibitem{C41}
Christoph Benzm{\"u}ller, Leon Weber, and Bruno Woltzenlogel~Paleo.
\newblock Computer-assisted analysis of the {Anderson-H\'{a}jek} ontological
  controversy.
\newblock In Ricardo~Souza Silvestre and Jean-Yves B\'eziau, editors, {\em
  Handbook of the 1st World Congress on Logic and Religion, Joao Pessoa,
  Brasil}, pages 53--54, 2015.
\newblock (superseded by 2016 article in Logica Universalis).

\bibitem{J32}
Christoph Benzm{\"u}ller, Leon Weber, and Bruno Woltzenlogel~Paleo.
\newblock Computer-assisted analysis of the {Anderson-H\'{a}jek} controversy.
\newblock {\em Logica Universalis}, 11(1):139--151, 2017.

\bibitem{J28}
Christoph Benzm\"uller and Bruno Woltzenlogel~Paleo.
\newblock {G{\"o}del's God in Isabelle/HOL}.
\newblock {\em Archive of Formal Proofs}, 2013.
\newblock (Formally verified).

\bibitem{W50}
Christoph Benzm\"uller and Bruno Woltzenlogel~Paleo.
\newblock {G\"odel's} {God} on the computer.
\newblock In S.~Schulz, G.~Sutcliffe, and B.~Konev, editors, {\em Proceedings
  of the 10th International Workshop on the Implementation of Logics}, 2013.
\newblock (Invited paper).

\bibitem{C40}
Christoph Benzm{\"u}ller and Bruno Woltzenlogel~Paleo.
\newblock Automating {G\"{o}del's} ontological proof of {God}'s existence with
  higher-order automated theorem provers.
\newblock In Torsten Schaub, Gerhard Friedrich, and Barry O'Sullivan, editors,
  {\em ECAI 2014}, volume 263 of {\em Frontiers in Artificial Intelligence and
  Applications}, pages 93 -- 98. IOS Press, 2014.

\bibitem{C39}
Christoph Benzm{\"u}ller and Bruno Woltzenlogel~Paleo.
\newblock {G\"odel's} proof of {God's} existence.
\newblock In Jean-Yves Beziau and Katarzyna Gan-Krzywoszynska, editors, {\em
  Handbook of the World Congress on the Square of Opposition IV}, pages 22--23,
  2014.
\newblock (superseded by ECAI-2014 paper).

\bibitem{C52}
Christoph Benzm{\"u}ller and Bruno Woltzenlogel~Paleo.
\newblock Experiments in computational metaphysics: {G\"odel's} proof of god's
  existence.
\newblock In Subhash~C. Mishram, Ramgopal Uppaluri, and Varun Agarwal, editors,
  {\em Science \& Spiritual Quest, Proceedings of the 9th All India Students'
  Conference, 30th October -- 1 November, 2015, IIT Kharagpur, India}, pages
  23--40. Bhaktivedanta Institute, Kolkata, \url{www.binstitute.org}, 2015.
\newblock (Invited paper, superseded by article in Savijnanam).

\bibitem{C46}
Christoph Benzm{\"u}ller and Bruno Woltzenlogel~Paleo.
\newblock Higher-order modal logics: Automation and applications.
\newblock In Adrian Paschke and Wolfgang Faber, editors, {\em Reasoning Web.
  Web Logic Rules - 11th International Summer School 2015, Berlin, Germany,
  July 31 - August 4, 2015, Tutorial Lectures}, number 9203 in LNCS, pages
  32--74, Berlin, Germany, 2015. Springer.

\bibitem{C44}
Christoph Benzm{\"{u}}ller and Bruno Woltzenlogel~Paleo.
\newblock Interacting with modal logics in the {Coq} proof assistant.
\newblock In Lev~D. Beklemishev and Daniil~V. Musatov, editors, {\em Computer
  Science - Theory and Applications - 10th International Computer Science
  Symposium in Russia, {CSR} 2015, Listvyanka, Russia, July 13-17, 2015,
  Proceedings}, volume 9139 of {\em LNCS}, pages 398--411. Springer, 2015.

\bibitem{W55}
Christoph Benzm{\"u}ller and Bruno Woltzenlogel~Paleo.
\newblock On logic embeddings and {G\"odel's} {God}.
\newblock In Mihai Codescu, Razvan Diaconescu, and Ionut Tutu, editors, {\em
  Recent Trends in Algebraic Development Techniques: 22nd International
  Workshop, WADT 2014, Sinaia, Romania, September 4-7, 2014, Revised Selected
  Papers}, number 9563 in LNCS, pages 3--6, Sinaia, Romania, 2015. Springer.
\newblock (Invited paper).

\bibitem{C55}
Christoph Benzm{\"u}ller and Bruno Woltzenlogel~Paleo.
\newblock The inconsistency in {G{\"o}del's} ontological argument: A success
  story for {AI} in metaphysics.
\newblock In Subbarao Kambhampati, editor, {\em IJCAI 2016}, volume 1-3, pages
  936--942. AAAI Press, 2016.

\bibitem{B15}
Christoph Benzm{\"u}ller and Bruno Woltzenlogel~Paleo.
\newblock The modal collapse as a collapse of the modal square of opposition.
\newblock In Jean-Yves B\'{e}ziau and Gianfranco Basti, editors, {\em The
  Square of Opposition: A Cornerstone of Thought (Collection of papers related
  to the World Congress on the Square of Opposition IV, Vatican, 2014),
  \url{http://www.springer.com/us/book/9783319450612}}, Studies in Universal
  Logic. Springer International Publishing Switzerland, 2016.

\bibitem{C60}
Christoph Benzm{\"u}ller and Bruno Woltzenlogel~Paleo.
\newblock An object-logic explanation for the inconsistency in {G\"odel's}
  ontological theory (extended abstract, sister conferences).
\newblock In Malte Helmert and Franz Wotawa, editors, {\em KI 2016: Advances in
  Artificial Intelligence, Proceedings}, LNCS, pages 244--250, Berlin, Germany,
  2016. Springer.

\bibitem{J36}
Christoph Benzm{\"u}ller and Bruno Woltzenlogel~Paleo.
\newblock Experiments in {Computational Metaphysics}: {G\"odel's} proof of
  {God's} existence.
\newblock {\em Savijnanam: scientific exploration for a spiritual paradigm.
  Journal of the Bhaktivedanta Institute}, 9:43--57, 2017.

\bibitem{Coq}
Y.~Bertot and P.~Casteran.
\newblock {\em {Interactive Theorem Proving and Program Development}}.
\newblock Springer, 2004.

\bibitem{Sledgehammer}
J.C. Blanchette, S.~B\"ohme, and L.C. Paulson.
\newblock Extending {Sledgehammer} with {SMT} solvers.
\newblock {\em Journal of Automated Reasoning}, 51(1):109--128, 2013.

\bibitem{Nitpick}
J.C. Blanchette and T.~Nipkow.
\newblock Nitpick: A counterexample generator for higher-order logic based on a
  relational model finder.
\newblock In {\em Proc. of ITP 2010}, number 6172 in LNCS, pages 131--146.
  Springer, 2010.

\bibitem{Satallax}
C.E. Brown.
\newblock Satallax: An automated higher-order prover.
\newblock In {\em Proc. of IJCAR 2012}, number 7364 in LNAI, pages 111 -- 117.
  Springer, 2012.

\bibitem{ContemporaryBibliography}
R.~Corazzon.
\newblock Contemporary bibligraphy on the ontological proof
  (\url{http://www.ontology.co/biblio/ontological-proof-contemporary-biblio.htm}).

\bibitem{Fitting}
M.~Fitting.
\newblock {\em {Types, Tableaux and G\"odel's God}}.
\newblock Kluver Academic Press, 2002.

\bibitem{C65}
David Fuenmayor and Christoph Benzm{\"u}ller.
\newblock Automating emendations of the ontological argument in intensional
  higher-order modal logic.
\newblock In {\em KI 2017: Advances in Artificial Intelligence 40th Annual
  German Conference on AI}, LNAI. Springer, 2017.

\bibitem{J35}
David Fuenmayor and Christoph Benzm\"uller.
\newblock {Types, Tableaus and G{\"o}del's God in Isabelle/HOL}.
\newblock {\em Archive of Formal Proofs}, 2017.
\newblock Formally verified with Isabelle/HOL.

\bibitem{Goedel1970}
K.~G\"odel.
\newblock Ontological proof.
\newblock In {\em {Kurt G\"odel: Collected Works Vol. 3: Unpublished Essays and
  Letters}}. Oxford University Press, 1970.

\bibitem{GoedelNotes}
K.~G\"odel.
\newblock {\em Appendix A. Notes in Kurt G\"odel's Hand}, pages 144--145.
\newblock In  \cite{sobel2004logic}, 2004.

\bibitem{Hazen}
A.P. Hazen.
\newblock On g\"odel's ontological proof.
\newblock {\em Australasian Journal of Philosophy}, 76:361--377, 1998.

\bibitem{Hurd03first-orderproof}
J.~Hurd.
\newblock First-order proof tactics in higher-order logic theorem provers.
\newblock In {\em Design and Application of Strategies/Tactics in Higher Order
  Logics, NASA Tech. Rep. NASA/CP-2003-212448}, pages 56--68, 2003.

\bibitem{Isabelle}
T.~Nipkow, L.C. Paulson, and M.~Wenzel.
\newblock {\em {Isabelle/HOL: A Proof Assistant for Higher-Order Logic}}.
\newblock Number 2283 in LNCS. Springer, 2002.

\bibitem{ScottNotes}
D.~Scott.
\newblock {\em Appendix B. Notes in Dana Scott's Hand}, pages 145--146.
\newblock In  \cite{sobel2004logic}, 2004.

\bibitem{sobel2004logic}
J.H. Sobel.
\newblock {\em Logic and Theism: Arguments for and Against Beliefs in God}.
\newblock Cambridge U. Press, 2004.

\bibitem{J22}
G.~Sutcliffe and C.~Benzm{\"u}ller.
\newblock Automated reasoning in higher-order logic using the {TPTP THF}
  infrastructure.
\newblock {\em Journal of Formalized Reasoning}, 3(1):1--27, 2010.

\bibitem{B66}
B.~Woltzenlogel~Paleo.
\newblock Leibniz's characteristica universalis and calculus ratiocinator
  today.
\newblock In Charles Tandy, editor, {\em Death and Anti-Death, Volume 14: Four
  Decades after Michael Polanyi, Three Centuries after G. W. Leibniz}. Ria
  University Press, 2016.

\bibitem{ComputationalPhilosophyRepository}
B.~Woltzenlogel~Paleo and C.~Benzm\"uller.
\newblock Computational philosophy repository
  (\url{https://gitlab.com/aossie/ComputationalPhilosophy/}).

\bibitem{FormalTheologyRepository}
B.~Woltzenlogel~Paleo and C.~Benzm\"uller.
\newblock Formal theology repository
  (\url{https://github.com/FormalTheology/GoedelGod}).

\end{thebibliography}

%\bibliographystyle{plain}
%\bibliography{Bibliography,chris}

%\printbibliography
